---
title: "Beer_Work"
author: "Emilee Skidgel"
date: "2023-03-09"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(rvest)
library(dplyr)
```

As an avid beer drinker, I often find myself wanting to try many different beers that I see at the liquor store. Due to lack of money and room in my fridge, I leave with just a single 6-pack of a new beer that I may or may not like. If only there was a way to purchase one pack of beer that has multiple types of beer inside...

A variety pack of new, cool, and the best beers in the world! 

### Top rated beers by style:

## Bocks
```{r echo=FALSE}
bock_link <- "https://www.beeradvocate.com/beer/top-styles/32/"
doppelbock_link <- "https://www.beeradvocate.com/beer/top-styles/35/"
eisbock_link <- "https://www.beeradvocate.com/beer/top-styles/36/"
maibock_link <- "https://www.beeradvocate.com/beer/top-styles/33/"
weizenbock_link <- "https://www.beeradvocate.com/beer/top-styles/92/"

# Bock
bocks <- read_html(bock_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

bocks <- read_html(bock_link) %>%
  html_table(header = TRUE) %>% 
  '[['(1)

bocks['Beer Type'] <- "Bock"

colnames(bocks) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
bocks <- bocks %>% select(-c('You'))

bocks$Name <- gsub("\\(|\\)", "", bocks$Name)
bocks$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", bocks$Name)
bocks <- tidyr::separate(bocks, Name, c("Beer Name", "Brewery"), sep = "_")

bocks <- bocks %>% select(-c('Brewery'))

# Doppelbock
doppelbocks <- read_html(doppelbock_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

doppelbocks <- read_html(doppelbock_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

doppelbocks['Beer Type'] <- "Doppelbock"

colnames(doppelbocks) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
doppelbocks <- doppelbocks %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

doppelbocks$Name <- gsub("\\(|\\)", "", doppelbocks$Name)
doppelbocks$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", doppelbocks$Name)
doppelbocks <- tidyr::separate(doppelbocks, Name, c("Beer Name", "Brewery"), sep = "_")

doppelbocks <- doppelbocks %>% select(-c('Brewery'))

# Eisbock
eisbocks <- read_html(eisbock_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

eisbocks <- read_html(eisbock_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

eisbocks['Beer Type'] <- "Eisbock"

colnames(eisbocks) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
eisbocks <- eisbocks %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

eisbocks$Name <- gsub("\\(|\\)", "", eisbocks$Name)
eisbocks$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", eisbocks$Name)
eisbocks <- tidyr::separate(eisbocks, Name, c("Beer Name", "Brewery"), sep = "_")

eisbocks <- eisbocks %>% select(-c('Brewery'))

# Maibock
maibocks <- read_html(maibock_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

maibocks <- read_html(maibock_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

maibocks['Beer Type'] <- "Maibock"

colnames(maibocks) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
maibocks <- maibocks %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

maibocks$Name <- gsub("\\(|\\)", "", maibocks$Name)
maibocks$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", maibocks$Name)
maibocks <- tidyr::separate(maibocks, Name, c("Beer Name", "Brewery"), sep = "_")

maibocks <- maibocks %>% select(-c('Brewery'))

# Weizenbock
weizenbocks <- read_html(weizenbock_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

weizenbocks <- read_html(weizenbock_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

weizenbocks['Beer Type'] <- "Weizenbock"

colnames(weizenbocks) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
weizenbocks <- weizenbocks %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

weizenbocks$Name <- gsub("\\(|\\)", "", weizenbocks$Name)
weizenbocks$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", weizenbocks$Name)
weizenbocks <- tidyr::separate(weizenbocks, Name, c("Beer Name", "Brewery"), sep = "_")

weizenbocks <- weizenbocks %>% select(-c('Brewery'))
```

## All bocks
```{r echo=FALSE}
all_bocks <- dplyr::bind_rows(bocks,
                              doppelbocks,
                              eisbocks,
                              maibocks,
                              weizenbocks)
```


## India Pale Ales
```{r echo=FALSE}
american_link <- "https://www.beeradvocate.com/beer/top-styles/116/"
belgian_link <- "https://www.beeradvocate.com/beer/top-styles/174/"
english_link <- "https://www.beeradvocate.com/beer/top-styles/150/"
imperial_link <- "https://www.beeradvocate.com/beer/top-styles/140/"
newengland_link <- "https://www.beeradvocate.com/beer/top-styles/189/"

# American IPA
american_ipa <- read_html(american_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

american_ipa <- read_html(american_link) %>%
  html_table(header = TRUE) %>% 
  '[['(1)

american_ipa['Beer Type'] <- "American IPA"

colnames(american_ipa) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
american_ipa <- american_ipa %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

american_ipa$Name <- gsub("\\(|\\)", "", american_ipa$Name)
american_ipa$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", american_ipa$Name)
american_ipa <- tidyr::separate(american_ipa, Name, c("Beer Name", "Brewery"), sep = "_")

american_ipa <- american_ipa %>% select(-c('Brewery'))

# Belgian IPA
belgian_ipa <- read_html(belgian_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

belgian_ipa <- read_html(belgian_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

belgian_ipa['Beer Type'] <- "Belgian IPA"

colnames(belgian_ipa) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
belgian_ipa <- belgian_ipa %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

belgian_ipa$Name <- gsub("\\(|\\)", "", belgian_ipa$Name)
belgian_ipa$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", belgian_ipa$Name)
belgian_ipa <- tidyr::separate(belgian_ipa, Name, c("Beer Name", "Brewery"), sep = "_")

belgian_ipa <- belgian_ipa %>% select(-c('Brewery'))

# English IPA
english_ipa <- read_html(english_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

english_ipa <- read_html(english_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

english_ipa['Beer Type'] <- "English IPA"

colnames(english_ipa) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
english_ipa <- english_ipa %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

english_ipa$Name <- gsub("\\(|\\)", "", english_ipa$Name)
english_ipa$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", english_ipa$Name)
english_ipa <- tidyr::separate(english_ipa, Name, c("Beer Name", "Brewery"), sep = "_")

english_ipa <- english_ipa %>% select(-c('Brewery'))

# Imperial IPA
imperial_ipa <- read_html(imperial_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

imperial_ipa <- read_html(imperial_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

imperial_ipa['Beer Type'] <- "Imperial IPA"

colnames(imperial_ipa) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
imperial_ipa <- imperial_ipa %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

imperial_ipa$Name <- gsub("\\(|\\)", "", imperial_ipa$Name)
imperial_ipa$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", imperial_ipa$Name)
imperial_ipa <- tidyr::separate(imperial_ipa, Name, c("Beer Name", "Brewery"), sep = "_")

imperial_ipa <- imperial_ipa %>% select(-c('Brewery'))

# New England IPA
newengland_ipa <- read_html(newengland_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

newengland_ipa <- read_html(newengland_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

newengland_ipa['Beer Type'] <- "New England IPA"

colnames(newengland_ipa) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
newengland_ipa <- newengland_ipa %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

newengland_ipa$Name <- gsub("\\(|\\)", "", newengland_ipa$Name)
newengland_ipa$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", newengland_ipa$Name)
newengland_ipa <- tidyr::separate(newengland_ipa, Name, c("Beer Name", "Brewery"), sep = "_")

newengland_ipa <- newengland_ipa %>% select(-c('Brewery'))

# All IPAs
all_ipas <- dplyr::bind_rows(american_ipa,
                              belgian_ipa,
                              english_ipa,
                              imperial_ipa,
                              newengland_ipa)
```

## Porters
```{r echo=FALSE}
american_porter_link <- "https://www.beeradvocate.com/beer/top-styles/159/"
baltic_porter_link <- "https://www.beeradvocate.com/beer/top-styles/80/"
english_porter_link <- "https://www.beeradvocate.com/beer/top-styles/101/"
imperial_porter_link <- "https://www.beeradvocate.com/beer/top-styles/192/"
smoked_porter_link <- "https://www.beeradvocate.com/beer/top-styles/194/"

# American Porter
american_porter <- read_html(american_porter_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

american_porter <- read_html(american_porter_link) %>%
  html_table(header = TRUE) %>% 
  '[['(1)

american_porter['Beer Type'] <- "American Porter"

colnames(american_porter) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
american_porter <- american_porter %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

american_porter$Name <- gsub("\\(|\\)", "", american_porter$Name)
american_porter$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", american_porter$Name)
american_porter <- tidyr::separate(american_porter, Name, c("Beer Name", "Brewery"), sep = "_")

american_porter <- american_porter %>% select(-c('Brewery'))

# Baltic Porter
baltic_porter <- read_html(baltic_porter_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

baltic_porter <- read_html(baltic_porter_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

baltic_porter['Beer Type'] <- "Baltic Porter"

colnames(baltic_porter) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
baltic_porter <- baltic_porter %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

baltic_porter$Name <- gsub("\\(|\\)", "", baltic_porter$Name)
baltic_porter$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", baltic_porter$Name)
baltic_porter <- tidyr::separate(baltic_porter, Name, c("Beer Name", "Brewery"), sep = "_")

baltic_porter <- baltic_porter %>% select(-c('Brewery'))

# English IPA
english_porter <- read_html(english_porter_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

english_porter <- read_html(english_porter_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

english_porter['Beer Type'] <- "English Porter"

colnames(english_porter) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
english_porter <- english_porter %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

english_porter$Name <- gsub("\\(|\\)", "", english_porter$Name)
english_porter$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", english_porter$Name)
english_porter <- tidyr::separate(english_porter, Name, c("Beer Name", "Brewery"), sep = "_")

english_porter <- english_porter %>% select(-c('Brewery'))

# Imperial Porter
imperial_porter <- read_html(imperial_porter_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

imperial_porter <- read_html(imperial_porter_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

imperial_porter['Beer Type'] <- "Imperial Porter"

colnames(imperial_porter) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
imperial_porter <- imperial_porter %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

imperial_porter$Name <- gsub("\\(|\\)", "", imperial_porter$Name)
imperial_porter$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", imperial_porter$Name)
imperial_porter <- tidyr::separate(imperial_porter, Name, c("Beer Name", "Brewery"), sep = "_")

imperial_porter <- imperial_porter %>% select(-c('Brewery'))

# Smoked Porter
smoked_porter <- read_html(smoked_porter_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

smoked_porter <- read_html(smoked_porter_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

smoked_porter['Beer Type'] <- "Smoked Porter"

colnames(smoked_porter) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
smoked_porter <- smoked_porter %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

smoked_porter$Name <- gsub("\\(|\\)", "", smoked_porter$Name)
smoked_porter$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", smoked_porter$Name)
smoked_porter <- tidyr::separate(smoked_porter, Name, c("Beer Name", "Brewery"), sep = "_")

smoked_porter <- smoked_porter %>% select(-c('Brewery'))

# All porters
all_porters <- dplyr::bind_rows(american_porter,
                              baltic_porter,
                              english_porter,
                              imperial_porter,
                              smoked_porter)

```
 
## Stouts 

```{r echo=FALSE}
american_imperial_link <- "https://www.beeradvocate.com/beer/top-styles/157/"
american_stout_link <- "https://www.beeradvocate.com/beer/top-styles/158/"
english_stout_link <- "https://www.beeradvocate.com/beer/top-styles/13/"
irish_dry_stout_link <- "https://www.beeradvocate.com/beer/top-styles/162/"
oatmeal_stout_link <- "https://www.beeradvocate.com/beer/top-styles/69/"

# American Imperial Stout
american_imperial <- read_html(american_imperial_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

american_imperial <- read_html(american_imperial_link) %>%
  html_table(header = TRUE) %>% 
  '[['(1)

american_imperial['Beer Type'] <- "American Imperial Stout"

colnames(american_imperial) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
american_imperial <- american_imperial %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

american_imperial$Name <- gsub("\\(|\\)", "", american_imperial$Name)
american_imperial$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", american_imperial$Name)
american_imperial <- tidyr::separate(american_imperial, Name, c("Beer Name", "Brewery"), sep = "_")

american_imperial <- american_imperial %>% select(-c('Brewery'))

# American Stout
american_stout <- read_html(american_stout_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

american_stout <- read_html(american_stout_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

american_stout['Beer Type'] <- "American Stout"

colnames(american_stout) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
american_stout <- american_stout %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

american_stout$Name <- gsub("\\(|\\)", "", american_stout$Name)
american_stout$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", american_stout$Name)
american_stout <- tidyr::separate(american_stout, Name, c("Beer Name", "Brewery"), sep = "_")

american_stout <- american_stout %>% select(-c('Brewery'))

# English Stout
english_stout <- read_html(english_stout_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

english_stout <- read_html(english_stout_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

english_stout['Beer Type'] <- "English Stout"

colnames(english_stout) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
english_stout <- english_stout %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

english_stout$Name <- gsub("\\(|\\)", "", english_stout$Name)
english_stout$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", english_stout$Name)
english_stout <- tidyr::separate(english_stout, Name, c("Beer Name", "Brewery"), sep = "_")

english_stout <- english_stout %>% select(-c('Brewery'))

# Irish Dry Stout
irish_dry_stout <- read_html(irish_dry_stout_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

irish_dry_stout <- read_html(irish_dry_stout_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

irish_dry_stout['Beer Type'] <- "Irish Dry Stout"

colnames(irish_dry_stout) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
irish_dry_stout <- irish_dry_stout %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

irish_dry_stout$Name <- gsub("\\(|\\)", "", irish_dry_stout$Name)
irish_dry_stout$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", irish_dry_stout$Name)
irish_dry_stout <- tidyr::separate(irish_dry_stout, Name, c("Beer Name", "Brewery"), sep = "_")

irish_dry_stout <- irish_dry_stout %>% select(-c('Brewery'))

# Oatmeal Stout
oatmeal_stout <- read_html(oatmeal_stout_link) %>%
  html_elements("td.hr_bottom_light a[href*='beer/profile'] b") %>%
  html_text()

oatmeal_stout <- read_html(oatmeal_stout_link) %>% 
  html_table(header = TRUE) %>% 
  '[['(1)

oatmeal_stout['Beer Type'] <- "Oatmeal Stout"

colnames(oatmeal_stout) <- c('Rank', 'Name', 'Ratings', 'Avg', 'You', 'Beer Type')
oatmeal_stout <- oatmeal_stout %>% select(-c('Rank', 'Ratings', 'Avg', 'You'))

oatmeal_stout$Name <- gsub("\\(|\\)", "", oatmeal_stout$Name)
oatmeal_stout$Name <- gsub("([a-z])([A-Z])", "\\1_\\2", oatmeal_stout$Name)
oatmeal_stout <- tidyr::separate(oatmeal_stout, Name, c("Beer Name", "Brewery"), sep = "_")

oatmeal_stout <- oatmeal_stout %>% select(-c('Brewery'))

# All stouts
all_stouts <- dplyr::bind_rows(american_imperial,
                              american_stout,
                              english_stout,
                              irish_dry_stout,
                              oatmeal_stout)
```

Now that I have all of the beer available, let's join them all together to begin creating variety packs. 

```{r echo=FALSE}
all_beers <- dplyr::bind_rows(all_bocks,
                              all_ipas,
                              all_porters,
                              all_stouts)
```

Let's get packing. 

```{r echo=FALSE}
library(tidyverse)
```

```{r echo=FALSE}
beer_picker <- function(bocks_n, ipas_n, porters_n, stouts_n) {
  #bocks
  bocks_sample <- sample(1:nrow(all_bocks), bocks_n)
  bname <- all_bocks$`Beer Name`[bocks_sample]
  btype <- all_bocks$`Beer Type`[bocks_sample]
  
  #ipas
  ipas_sample <- sample(1:nrow(all_ipas), ipas_n)
  iname <- all_ipas$`Beer Name`[ipas_sample]
  itype <- all_ipas$`Beer Type`[ipas_sample]
  
  #porters
  porters_sample <- sample(1:nrow(all_porters), porters_n)
  pname <- all_porters$`Beer Name`[porters_sample]
  ptype <- all_porters$`Beer Type`[porters_sample]
  
  #stouts
  stouts_sample <- sample(1:nrow(all_stouts), stouts_n)
  sname <- all_stouts$`Beer Name`[stouts_sample]
  stype <- all_stouts$`Beer Type`[stouts_sample]
  
  beer_df <- data.frame(Name = c(bname, iname, pname, sname), Type = c(btype, itype, ptype, stype))
  
}
```

## INTERACTIVE INPUT
This is the interactive portion.

```{r echo=FALSE}
# Variety pack
variety_pack <- beer_picker(1,2,2,1)
variety_pack

# Bock pack
bock_pack <- beer_picker(6,0,0,0)
bock_pack

# IPA pack
ipa_pack <- beer_picker(0,6,0,0)
ipa_pack

# Porter pack
porter_pack <- beer_picker(0,0,6,0)
porter_pack

stout_pack <- beer_picker(0,0,0,6)
stout_pack
```



